\section{Issues}

\TODO{no title}
\TODO{you do not use ``quotes'' properly}
\TODO{you need to {\em emphasize} and not ``quote''}
\TODO{this is cool}


\TODO{Have you written the report in the speciﬁed format?}
\TODO{Have you included an acknowledgement section?}
\TODO{Have you included the paper in the submission system (In our class it is git)?}
\TODO{Have you speciﬁed proper identiﬁcation in the submission system. THis is typically a form or ASCII text that needs to be ﬁlled out (In our case it is a README.md ﬁle that includes a homework ID, names of the authors, and e-mails)?}
\TODO{Have you included all images in native and PDF format in the submission system?}
\TODO{Have you added the bibliography ﬁle that you managed (In our case jabref to make it simple for you)?}
\TODO{In case you used word have you also provided the jabref?}
\TODO{In case of a class and if you do a multi-author paper, have you added an appendix describing who did what in the paper?}
\TODO{Have you spellchecked the paper?}
\TODO{Are you usingaandtheproperly?}
\TODO{Have you made sure you do not plagiarize?}
\TODO{Is the title properly capitalized?}
\TODO{Have you not used phrases such as shown in the Figure below, but instead used as shown in Figure 3 when referring to the 3rd ﬁgure?}
\TODO{Have you capitalized “Figure 3”, “Table 1”, ... ?}
\TODO{Have you removed any ﬁgure that is not referred explicitly in the text (As shown in Figure ..)}
\TODO{Are the ﬁgure captions bellow the ﬁgures and not on top. (Do not include the titles of the ﬁgures in the ﬁgure itself but instead use the caption or that information?}
\TODO{When using tables have you put the table caption on top?}
\TODO{Make the ﬁgures large enough so we can read the details. If needed make the ﬁgure over two columns?}
\TODO{Do not worry about the ﬁgure placement if they are at a different location than you think. Figures are allowed to ﬂoat. If you want you can place all ﬁgures at the end of the report?}
\TODO{Are all ﬁgures and tables at the end?}
\TODO{In case you copied a ﬁgure from another paper you need to ask for copyright permission. IN case of a class paper youmustinclude a reference to the original in the caption.}
\TODO{Do not use the word “I” instead use we even if you are the sole author?}
\TODO{Do not use the phrase “In this paper/report we show” instead use “We show”. It is not important if this is a paper or a report and does not need to be mentioned.}
\TODO{Do not artiﬁcially inﬂate your paper if you are bellow the page limit and have nothing to say anymore.}
\TODO{ If your paper limit is 12 pages but you want to hand in 120 pages, please check ﬁrst ;-)}
\TODO{Donotusethecharacters \& \# \% \_ put a bakslash berfore them}
\TODO{If you want to say and do not use \& but use the word and.}
\TODO{Latex uses double single open quotes and double single closed quotes for quotes. Have you made sure you replaced them?}
\TODO{Pasting and copying from the Web often results in non ascii characters to be used in your text, please remove them and replace accordingly.}




